Analysis after review

### 2020-04-29 reports/DRM_exp/analysis_DRM_after_review.Rmd
new R2 and glmm models

  rnk <- rank(dfxx_notgt$min_tgt_dist_no0)

@@

```{r}
df2_modelmem1 <- 
  df2_modelmem %>% 
    ungroup() %>% 
    select(subject_id, trial_id, category_centroid_type = type, memorability_model =model_type, correct)

df2_modeldisttoproto31 <- 
  df2_modeldisttoproto3  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, dist_to_proto3 =model_type, correct)

df2_modeldisttoproto51 <- 
  df2_modeldisttoproto5  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, dist_to_proto5 =model_type, correct)

df2_tgt_modeldist1 <- 
  df2_tgt_modeldist  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, min_dist_to_tgt =model_type, correct) 
df_models_res <- df2_modelmem1 %>% 
  left_join(df2_modeldisttoproto31, by = c("subject_id", "trial_id", "correct")) %>% 
  left_join(df2_modeldisttoproto51, by = c("subject_id", "trial_id", "correct")) %>% 
  left_join(df2_tgt_modeldist1, by = c("subject_id", "trial_id", "correct")) %>% 
  filter(category_centroid_type != "target")

@@

XXtab <- df_models_res_longer %>% 
  group_by(name,value) %>% 
  summarize(FA = sprintf("%.2f (%.2f)", mean(1-correct),sd(1-correct)))

@@

lm_orig_model <- df_models_res %>% lm(correct~category_centroid_type,.)
lm_dist_to_tgt <- df_models_res %>% lm(correct~min_dist_to_tgt,.)
lm_dist_to_proto_conv5 <- df_models_res %>% lm(correct~dist_to_proto5,.)
lm_dist_to_proto_conv3 <- df_models_res %>% lm(correct~dist_to_proto3,.)
lm_memorability <- df_models_res %>% lm(correct~memorability_model,.)
models_list <- list(lm_orig_model,lm_dist_to_tgt,lm_dist_to_proto_conv5,lm_dist_to_proto_conv3,lm_memorability)
models_list %>% 
  map(summary) %>%
  map_dbl("r.squared") %>% 
  round(2)

>>>>

  rnk <- rank(dfxx_notgt$min_tgt_dist)

@@

```{r}
df2_modelmem1 <- 
  df2_modelmem %>% 
    ungroup() %>% 
    select(subject_id, trial_id, category_centroid_type = type, memorability_model =model_type, correct, category)

df2_modeldisttoproto31 <- 
  df2_modeldisttoproto3  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, dist_to_proto3 =model_type, correct, category)

df2_modeldisttoproto51 <- 
  df2_modeldisttoproto5  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, dist_to_proto5 =model_type, correct, category)

df2_tgt_modeldist1 <- 
  df2_tgt_modeldist  %>% 
    ungroup() %>% 
    select(subject_id, trial_id, min_dist_to_tgt =model_type, correct, category) 
df_models_res <- df2_modelmem1 %>% 
  left_join(df2_modeldisttoproto31, by = c("subject_id", "trial_id", "correct","category")) %>% 
  left_join(df2_modeldisttoproto51, by = c("subject_id", "trial_id", "correct","category")) %>% 
  left_join(df2_tgt_modeldist1, by = c("subject_id", "trial_id", "correct","category")) %>% 
  filter(category_centroid_type != "target")

@@

XXtab <- df_models_res_longer %>% 
  group_by(name,value) %>% 
  summarize(FA = sprintf("%.2f", mean(1-correct)))

@@

glmm_null_model <- df_models_res %>% glmer(correct~1+(1|subject_id) + (1|category), ., family = binomial())

glmm_orig_model <- df_models_res %>% glmer(correct~category_centroid_type+(1+category_centroid_type|subject_id) + (1|category), ., family = binomial())
glmm_dist_to_tgt <- df_models_res %>% glmer(correct~min_dist_to_tgt + (1+min_dist_to_tgt|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv5 <- df_models_res %>% glmer(correct~dist_to_proto5 + (1+dist_to_proto5|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv3 <- df_models_res %>% glmer(correct~dist_to_proto3 + (1+dist_to_proto3|subject_id) + (1|category),., family = binomial())
glmm_memorability <- df_models_res %>% glmer(correct~memorability_model + (1+memorability_model|subject_id) + (1|category),., family = binomial())
models_list <- list(glmm_null_model,glmm_orig_model,glmm_dist_to_tgt,glmm_dist_to_proto_conv5,glmm_dist_to_proto_conv3,glmm_memorability)
models_list %>% 
  map(performance::r2_nakagawa) %>%
  map_dbl("R2_conditional") %>% 
  round(2)

models_list %>% 
  map(performance::r2_nakagawa) %>%
  map_dbl("R2_marginal") %>% 
  round(2)
